\input{preamble.tex}
\begin{document}

\section{Introduction}
A domain $\Omega\subseteq\C$ is called \textbf{quasiconvex }if its
intrinsic metric is comparable to the ambient Euclidean metric. Explicitly,
this means that there exists a constant $A\geq1$ such that every
two points $z_{1},z_{2}\in\Omega$ have a rectifiable path $\gamma:\left[0,1\right]\to\Omega$
connecting them which satisfies
\[
\Length(\gamma)\leq A\cdot\left|z_{1}-z_{2}\right|.
\]
We call such a path $\gamma$ a \emph{quasiconvexity certificate for
$z_{1}$ and $z_{2}$}.
% or "witness"

If $\Omega$ is the interior of a Jordan curve, then by \cite[Corollary F]{hakobyan_euclidean_2008}
it is enough to find certificates for points $z_{1},z_{2}$ that are
on the boundary curve $\partial\Omega$.%
\begin{comment}
It is also shown in \cite{hakobyan_euclidean_2008} that any quasidisk is quasiconvex.
\end{comment}

The \emph{cauliflower} is the filled Julia set of the map $z^2+\frac 14$.
We show that its complement, $\mathrm{Exterior}(\mathcal{J}(z^{2}+1/4))$,
is quasiconvex. We then adapt our argument to establish that the exterior of the developed deltoid is quasiconvex.

One motivation to study quasiconvexity stems from its connection with the
John property: If $\Omega$ is a quasiconvex Jordan domain, then its complement has a John interior. See \cite[Corollary 3.4]{hakobyan_euclidean_2008} for a proof.
As a consequence, this result is a strengthening of \cite[Theorem 6.1]{carleson_julia_1994}, which shows that the cauliflower is a John domain directly.

This result also has a function-theoretic interpretation: By \cite[Theorem 1.1]{koskela_geometric_2010}, it shows that the cauliflower is a BV-extension domain.
% A bounded, simply connected planar domain is a BV-extension domain if and only if its complement is quasiconvex.

\begin{comment}
The Filled Julia set of $z^{2}+1/4$, called the cauliflower, has
an inward-pointing cusp and hence is not quasiconvex.
\end{comment}

\begin{comment}
Thus, for any $c$ in 

For values $c$ in quadratic polynomials $f_{c}(z)=z^{2}+c$
\end{comment}
\begin{comment}
If $f_{c}$ has an attracting fixed point then its Julia set $\mathcal{J}(f_{c})$
is a quasicircle, hence its interior and exterior are both quasiconvex.
This is the case for values of $c$ in the main cardioid of the Mandelbrot
set.
, i.e.\ for 
\[
c\in\left\{ -\frac{\lambda}{2}-\frac{\lambda^{2}}{4}:\,\left|\lambda\right|<1\right\} .
\]
\end{comment}

\subsection{Sketch of the argument}

We show quasiconvexity by an explicit construction of a certificate connecting two given points on the Julia set.

We first build certificates for the exterior unit disk $\mathbb D ^*$ and then transport them by the Böttcher coordinate $\psi$ of $f_{1/4}$ to the exterior of the cauliflower.

In order to retain control on the certificates after applying $\psi$, we build the certificates on $\mathbb D^*$ in a manner invariant under the map $f_0: z\mapsto z^2$. This is done by only traveling along the boundaries of Carleson boxes in $\mathbb D^{*}$. 

The image of a certificate $c$ in $\mathbb D^{*}$ under the conjugacy $\psi$ is invariant under $f_{1/4}$. We use this invariance to show that $\psi(c)$ is indeed a certificate, by employing a parabolic variant of the principle of the conformal elevator: We repeatedly apply $f_{1/4}$ on $\psi(c)$ until either the distance between the endpoints grows to a definite size or one endpoint is attracted sufficiently quickly to the parabolic fixed point $1/2$. The latter case requires a more delicate treatment.

To facilitate the reading, we separate this latter difficulty by first demonstrating the proof in the hyperbolic case of maps $f_c$ where  $c\in\left(-\frac 34,\frac{1}{4}\right)$. In this case the usual conformal elevator applies. We then treat the $c=\frac 14$ case.

% Although $J_{0.1}^{\text{exterior}}$ is known in advance to be quasiconvex, in virtue of being a quasidisk.


\section{The exterior disk}

\begin{comment}
The exterior $\D^{*}=\left\{ \left|z\right|>1\right\} $ of the unit
disk is trivially quasiconvex by connecting points along the perimeter of the circle. However, these paths follow the boundary closely and their length would blow up if we transport them to the exterior of $\mathcal{J}(f_{c})$, $c\neq0$, via the Riemann map. Instead,
\end{comment}

We connect boundary points by moving along the boundaries of Carleson boxes which we now define.
\begin{definition}
Let $n\in\N_{0}$ and $k\in\left\{ 0,\ldots,2^{n}-1\right\} $. We
call the set
%\[B_{n,k}=\exp\left(\biggl(2^{-n-1}\log2,\,2^{-n}\log2\biggl]\times\biggl(\frac{k}{2^{n}}2\pi,\,\frac{(k+1)}{2^{n}}2\pi\biggl]\right)\]

\[
B_{n,k}=\left\{ z:\quad\left|z\right|\in\biggl(2^{2^{-n}},2^{2^{-n-1}}\biggl],\qquad\mathrm{arg}(z)\in\biggl(\frac{k}{2^{n}}2\pi,\frac{(k+1)}{2^{n}}2\pi\biggl]\right\} 
\]
a \emph{Carleson box}\,.
Observe that for a fixed $n$, the union $\bigsqcup_{k=0}^{2^{n}-1}B_{k,n}$
is a partition of the annulus 
\[
\left\{ 2^{2^{-n-1}}<\left|z\right|\leq2^{2^{-n}}\right\} 
\]
 into $2^{n}$ equally-spaced sectors.
 
The \emph{Carleson box decomposition} is the partition of $\D^{*}$ which consists of $f_{0}$-Carleson
boxes:
\[
\D^{*}=\left\{ \zeta:\,\left|\zeta\right|>2\right\} \sqcup\bigsqcup_{n=0}^{\infty}\bigsqcup_{k=0}^{2^{n}-1}B_{n,k}.
\]
The crucial property of this decomposition is its invariance under $f_{0}$,
stemming from the relation
\begin{equation*}
f_{0}\left(B_{n+1,k}\right)=B_{n,\lfloor\frac{k}{2}\rfloor}.
\end{equation*}
\end{definition}

We describe the motion along Carleson boxes using the metaphor of a passenger who travels by trains. 
We now define \enquote{stations} and \enquote{tracks}.

\begin{definition}
A \emph{terminal} is a point $\zeta \in \partial \mathbb D^*$ on the unit circle.
The \emph{central station} is the point\emph{ $s_{0,0}=2$. Stations
}are the iterated preimages of the central station under the map $f_{0}:\zeta\mapsto \zeta^{2}$.
We index them as 
\[
s_{n,k}=2^{2^{-n}}\exp\left(\frac{k}{2^{n}}2\pi i\right),\qquad n\in\N_{0},\quad k\in\left\{ 0,\ldots,2^{n}-1\right\} .
\]

Stations are naturally structured in a binary tree, where the root is the central station and the children of a node are its preimages. The \emph{generation} of a station $s_{n,k}$ is its level $n$ in this tree. The $2^{n}$ stations of generation $n$ in the tree are equally spaced on the circle $C_{n}=\left\{ \left|\zeta\right|=2^{1/2^{n}}\right\} $. 
\end{definition}

We next lay two types of \enquote{rail tracks} on the boundaries of Carleson boxes, which we use to travel between stations.

\begin{definition}
Let $s=s_{n,k}$ be a station.

1. The \emph{peripheral neighbors} of $s$ are the two stations $s_{n,\left(k\pm1\right)\mod2^{n}}$ adjacent to $s_{n,k}$ on $C_{n}$.

2. Given a peripheral neighbor $s'$ of $s$, the \emph{peripheral
	track }$\gamma_{s,s'}$ from $s$ to $s'$
is the short arc of the circle $C_{n}$ connecting $s$ to $s'$.

3. The \emph{radial successor} of $s$ is $\RadialSuccessor(s)=s_{n+1,2k}$, the unique station of generation $n+1$ on the radial segment $[0,s]$.

4. Denote $s'=\RadialSuccessor(s)$, then the \emph{Express track} $\gamma_{s,s'}$ from $s$ to $s'$ is the radial segment $[s,s']$.

%5. An \emph{itinerary} is a sequence of stations $\left(\sigma_{0},\sigma_{1},\ldots\right)$. We identify an itinerary with the curve obtained by traveling along it.
\end{definition}

Notice that the tracks preserve the dynamics: applying $f_0$ to a peripheral track between stations $s,s'$ gives a peripheral track between the parents of $s,s'$ in the tree, and likewise for an express track.

When a passenger travels between two stations $s_1$ and $s_2$, they must follow a particular itinerary from $s_1$ to $s_2$.
If $s_1$ is the central station, then this compulsory itinerary is determined by the rule that the passenger always stays as close as possible to its destination $s_2$ in the peripheral distance. 
This also determines how to travel from the central station to a terminal $\zeta\in \partial \mathbb D^*$, by continuity. See \cref{fig:Carleson1} and the next definition.

% There is a caveat in the analogy, because this gives rise to an itinerary between any two points and if we approximate terminal points by bearby stations then we do not get the same path.

\begin{definition}
Let $\zeta=\exp(2\pi i\theta)\in\partial\D$. The \emph{itinerary} $\eta_\zeta$ from the central station to $\zeta$ is a path 
$\eta_\zeta = \gamma _{\sigma_0,\sigma_1} + \gamma_{\sigma_1,\sigma_2}+\ldots$ made of tracks between stations $\sigma_0,\sigma_1,\ldots$, defined inductively as follows:

Start at the main station $\sigma_0=s_{0,0}$. Suppose that we already chose $\sigma_0,\ldots,\sigma_k$. If there is a peripheral neighbor $\sigma$ of $\sigma_k$ that is closer peripherally to $\zeta$, meaning that $$\left|\Arg\left(\zeta\right)-\Arg\left(\sigma\right)\right|
< \left|\Arg\left(\zeta\right)-\Arg\left(\sigma_{k}\right)\right|,$$ then take $\sigma_{k+1}=\sigma$. Otherwise, take 
$\sigma_{k+1}=\RadialSuccessor(\sigma)$.
\end{definition}

\input{"marker path.tex"}

We call $\eta_{\zeta}$ the \emph{central itinerary} of $\zeta$ and identify $\eta_{\zeta}$ with its sequence of stations $(\sigma_0,\ldots)$. We record two properties of central itineraries:

\begin{itemize}
	\item There are no two consecutive peripheral tracks in $\eta_{\zeta}$ and thus
	\begin{equation} \label{generation-lower-bound}
		\operatorname{Generation}(\sigma_k)\geq \frac k2.
	\end{equation}
%	where as before the generation of $s_{n,k}$ is defined to be $n$.
	
	\item Central itineraries are essentially invariant under $f_{0}$, in the sense that
	\begin{equation*}
		f_{0}(\eta_{\zeta})=\eta{}_{f_{0}(\zeta)}\cup[s_{0,0},f_0(s_{0,0})]
	\end{equation*}
	for every $\zeta\in \partial \mathbb D^*$.
\end{itemize}

\begin{lemma} \label{track_decay}
Let $\zeta\in \partial \mathbb D^*$. Decompose the central itinerary $\eta_{\zeta}$ into its constituent tracks, 
$$\eta_{\zeta}=\gamma _1 + \gamma_2 + \dots,$$ 
	then we have the estimate $$\Length(\gamma_{k})\lesssim 2^{-k},$$ uniformly in $\zeta$. 
In particular, the total length of $\eta_\zeta$ is bounded uniformly in $\zeta$.
\end{lemma}


%In particular, the length of a suffix $\sigma_{k}+\sigma_{k+1}+\ldots$ decays exponentially in $k$, uniformly in $\zeta$.

%Note that this may result in an "inefficient" itinerary: two stations that are peripheral neighbors might have a rather long itinerary between them.
%By continuity, this defines the itinerary between any two terminals $\zeta_1$ and $\zeta_2$:

% If two terminals are bearby then their common ancestor $N$ must be large, because if $N$ is small then the points must be far away.*/-+

\begin{definition} \label{def-disk-itinerary} Given two distinct terminals $\zeta_{1},\zeta_{2}\in\partial\D^*$, form the central itineraries $\eta_{\zeta_{1}}=\left(\sigma_{n}^{1}\right)_{n=0}^{\infty}$ and 
	$\eta_{\zeta_{2}}=\left(\sigma_{n}^{2}\right)_{n=0}^{\infty}$
	 and let  $\sigma=\sigma^1_i=\sigma^2_j$ be the last station that is in both $\eta_{\zeta_{1}}$ and $\eta_{\zeta_{2}}$. %Note that $\sigma$ is well-defined.
	 We define the \emph{itinerary} between  $\zeta_{1}$ and $\zeta_{2}$ to be the path  %$\eta_{\zeta_{i}}^{\text{truncated}}=\left(\sigma_{N},\sigma_{N+1}^{i},\ldots\right)$ be the truncated paths. Then
 \begin{gather*}
 \eta_{\zeta_{1},\zeta_{2}}=  \left(\dots,\sigma_{i+2}^{1},\sigma_{i+1}^{1},\sigma,\sigma_{j+1}^{2},\sigma_{j+2}^{2},\dots\right).
 \end{gather*}
	This is a simple bi-infinite path connecting $\zeta_{1}$ and $\zeta_{2}$, see \cref{fig:Carleson2}. Note that itineraries are equivariant under the dynamics: we have  \begin{equation}
		f(\eta_{\zeta_1,\zeta_2})=\eta_{f(\zeta_1),f(\zeta_2)}
	\end{equation} for every pair of terminals $\zeta_1,\zeta_2 \in \partial \mathbb D^*$.
	
	
\end{definition}
\input{"marker path 2.tex"}

\begin{theorem} \label{quasiconvex disk}
The domain $\D^{*}$ is quasiconvex with the itineraries $\eta_{\zeta_1,\zeta_2}$ as certificates.
\end{theorem}

\begin{proof}
We keep the notations of \cref{def-disk-itinerary}.
We decompose the itinerary into two paths, so that
\begin{equation}
\Length(\eta_{\zeta_{1},\zeta_{2}})=\Length\left(\sigma,\sigma_{j+1}^{2},\sigma_{j+2}^{2},\dots\right)
+\Length\left(\sigma,\sigma_{i+1}^{1},\sigma_{i+2}^{1},\dots\right),
\end{equation}
and bound each summand using \cref{track_decay}. Denoting $\operatorname{Generation}(\sigma)=n$, we obtain
\begin{align*}
\Length(\eta_{\zeta_{1},\zeta_{2}})
&\lesssim 2 \sum_{k=n}^{\infty}\frac{1}{2^{k}} 
\lesssim2^{-n}. \label{eq:1}
\end{align*}
We conclude by noticing that
\begin{align*}
\left|\zeta_{1}-\zeta_{2}\right|
&\asymp
\left|\Arg\left(\zeta_{1}\right)-\Arg\left(\zeta_{2}\right)\right|\\
&\geq \frac {2\pi}{2^{n+2}}\\
&\gtrsim 	\Length\left(\eta_{\zeta_{1},\zeta_{2}}\right).
\end{align*}
%Suppose two stations diverge at generation $N$ and never meet after that. Then we can bound the distance between the endpoints from below. This is not quite as trivial as it sounds but it is correct.
\end{proof}

	
\section{Transporting the Rails} \label{rails-section}
Let $c\in\left[-\frac 34,\frac{1}{4}\right]$ and denote by $\psi$ the Böttcher coordinate of $f: z\mapsto z^2+c$ at infinity. 
This means that $\psi$ is the unique conformal map $\D^{*}\to\mathrm{Exterior}(\mathcal{J})$  which fixes $\infty$ and satisfies the conjugacy $$f\circ\psi=\psi\circ f_{0}.$$
Since the Julia set $\mathcal J$ is a Jordan curve, the map $\psi$ extends to a homeomorphism between the circle $\partial\D$ and the Julia set $\mathcal{J}(f)$ by Carathéodory's
theorem.

We apply $\psi$ to the rails that we constructed in $\mathbb D^*$ to obtain the corresponding rails in $\mathrm{Exterior}(\mathcal{J})$:
\begin{definition} \leavevmode
\begin{enumerate}
	\item The 	\emph{stations} of $f_c$ are the points  $s_{n,k,c}=\psi(s_{n,k})$.


\item The \emph{$c$-tracks} are the curves of the form $\psi \left(\gamma_{s,s'}\right)$, where $\gamma_{s,s'}$ is a track. They are classified as express or peripheral according to the corresponding classification of $\gamma_{s,s'}$. 
Express tracks lie on \emph{external} rays of the filled Julia set $\mathcal K$, while peripheral tracks lie on the equipotentials of $\mathcal K$.

\item Let $z_1,z_2\in \mathcal J$ and let $\zeta_i=\psi^{-1}(z_i)$ be the corresponding points on $\partial \mathbb D^*$. 
The \emph{$c$-itineraries} are $\eta_{z,z'}=\psi(\eta_{\zeta,\zeta'})$.
\end{enumerate}

We omit $c$ from the notation for ease of reading. It will be clear from the context whether we work in $\mathbb D^*$ or in $\mathrm{Exterior}(\mathcal J)$.

%These itineraries can equivalently be obtained directly as in the case of $\mathbb D^*$, in terms of following the central itineraries from the common ancestor in the tree structure.
%Trivially since $\psi$ is a bijective correspondence between the two decompositions.
\end{definition}

Note that $\psi\left((1,\infty)\right)\subseteq\R$ since $\mathcal{J}$ is symmetric with respect to the real line. In particular $\psi(s_{0,0})\in\R$, i.e.\ the $c$-central station is real.

\begin{comment}
\begin{proof}
Formally, $\overline{\psi}(\overline{z})$
	is another conformal conjugacy between $f$ and $f_0$ which fixes infinity, so by uniqueness of the Böttcher coordinate we obtain $\psi(z)=\overline{\psi}(\overline{z})$,
	hence $\psi(z)\in\R$ for $z\in\R$.
\end{proof}
\end{comment}

\section{Hyperbolic Maps}

A rational map is \emph{hyperbolic} if every critical point converges to an attracting cycle.
Hyperbolic maps enjoy the principle of the conformal elevator, which roughly says that any ball centered on the Julia set can be blown up to a definite size. More precisely, we have the following:

\begin{proposition}[The Principle of the Conformal Elevator] \label{elevator}
	Let $f$ be a rational hyperbolic map, let $z\in \mathcal J$ be a point on the Julia set of $f$ and let $r>0$. Then there exists some forward iterate $f^{\circ n}$ of $f$ which is injective on the ball $B(z,2r)$ and such that
	$\diam {f^{\circ n}(B(z,r))}$ is bounded below uniformly in $z$ and $r$. 
\end{proposition}

%See \cite{bonk_quasisymmetries_2016} for a stronger version, details and a proof.

\begin{corollary} \label{elevator for points on julia}
	Let $f$ be a rational hyperbolic map. There exists  $\epsilon > 0$ such that every pair of points $z,w\in\mathcal{J}(f)$ has a forward iterate $f^{\circ n}$ for which $\left|f^{\circ n}(z)-f^{\circ n}(w)\right|>\epsilon$.	
\end{corollary}

\begin{comment}
\begin{proof}
	Apply \cref{elevator} to a ball centered on the Julia set which contains $z,w$ on its boundary at roughly antipodal points. After blowing up we get points $f^{\circ n}(z),f^{\circ n}(w)$ which are a definite distance apart by Koebe's distortion theorem. %\todo{make this correct}
\end{proof}
\end{comment}

We are now ready to show the analogue of \cref{quasiconvex disk}:
%\todo{We use more than hyperbolicity, also that the Julia set is a Jordan domain}
\begin{theorem}  \leavevmode
\begin{enumerate}[label=\normalfont(\roman*)]

\item Let $z\in\mathcal{J}$ and decompose its central itinerary into tracks, 
\begin{equation*}
\eta_z = \gamma _1 +\gamma_2 +\dots.
\end{equation*}
Then we have the estimate
\begin{equation*}
\Length(\gamma_{k})\lesssim\theta^{-k},
\end{equation*}
uniformly in $z$, for some constant $\theta=\theta(c)>1$. In particular, any point on \(\mathcal{J}\) can be reached from $s_{0,0}$ by a curve of bounded length.

\item The domain $\mathrm{Exterior}(\mathcal{J})$ is quasiconvex with the itineraries $\eta_{z_1,z_2}$ as certificates.
	\end{enumerate}
\end{theorem}

\begin{proof} \leavevmode
\begin{enumerate}[label=\normalfont(\roman*)]
\item The map $f$ has some iterate $f^{\circ N}$ such that $|f^{\circ N}|>1$ on the Julia set $\mathcal{J}$, where $N$ is independent of $z$.
By the compactness of $\mathcal J$, there is some $\theta >1$ such that $\left|(f^{\circ N})'\right|(z)>\theta$ on some neighborhood $\mathcal{U}$ of $\mathcal{J}$.
Since every itinerary is eventually contained in $\mathcal{U}$, for almost all itineraries $\gamma$ we have 
\begin{equation*}
\Length ( f^{\circ N}(\gamma) ) \geq \theta \cdot \Length( \gamma). 
\end{equation*}

The peripheral tracks on circles $C_n$ of index $n \equiv k$ modulo $N$ have a total length bounded by a geometric series of rate $\theta$, hence finite. 
The lengths of the express tracks can be bounded in the same way. % We conclude that the total length of the itinerary is bounded.

\item Since we already know that the lengths of tracks in the itinerary decay exponentially with rate $\theta>1$, the same proof of the case $c=0$ also shows quasiconvexity in this case.

We give a second proof, relying on \cref{elevator for points on julia}. This proof will better prepare us for the parabolic $c=1/4$ case, where we don't have expansion of $f$ on its Julia set.

By \cref{elevator for points on julia}, there exists an $\epsilon>0$ such that any two points are $\epsilon$-apart under some iterate $f$. 
Let $z_{1},z_{2}\in\mathcal{J}(f)$. If $\left|z_{1}-z_{2}\right|\geq\epsilon$ then there is nothing to
prove since the length of $\eta_{z_1z,_2}$ is bounded above by part (i).
% we may just concatenate $\eta_{z_{1}}$ and $\eta_{z_{2}}$ and absorb this bounded length into the quasiconvexity constant

\begin{comment}
Explicitly, if $\Length\left(\eta_{z}\right)\leq L$
for all $z\in\mathcal{J}$ then we take $A\geq\frac{2L}{\epsilon}$
and then automatically $\Length\left(\eta_{z_{1}}+\eta_{z_{2}}\right)\leq A\left|z_{1}-z_{2}\right|$.
\end{comment}

On the other hand, if $\left|z_{1}-z_{2}\right|<\epsilon$, then
we may use  \cref{elevator for points on julia} to find an iterate $f^{\circ n}$ such that 
\begin{equation}
	|w_1-w_2|:=\left|f^{\circ n}(z_{1})-f^{\circ n}(z_{2})\right|\geq\epsilon.
\end{equation}
Such itineraries $\eta_{w_1,w_2}$ are certificates, and it follows that the original itineraries $\eta_{z_1z,_2}$ are certificates by Koebe's distortion theorem, which implies that 
\begin{equation}
	\frac{\Length\left(\eta_{z_{0},z_{1}}\right)}{|z_1-z_2|}\asymp\frac{\Length\left(\eta_{w_0,w_1}\right)}{|w_1-w_2|}.
\end{equation}

\begin{comment}
By a distortion estimate
\begin{equation*}
\Length\left(\eta_{z_{0},z_{1}}\right)\asymp\frac{\Length\left(\eta_{w_0,w_1}\right)}{\left|\left(f^{\circ n}\right)'\left(\zeta\right)\right|}
\end{equation*}
 for some point $\zeta \in \mathcal{J}$. The denominator grows
with $n$ exponentially at rate $\theta$, while the numerator has
a bound of the form 
\[
\Length\left(\eta_{w_1,w_2}\right)\lesssim\left|w_1-w_2\right|\lesssim\theta^{n}\left|z_{1}-z_{2}\right|.
\]
Altogether 
\[
\Length\left(\eta_{z_{1},z_{2}}\right)\lesssim\frac{\theta^{n}\left|z_{1}-z_{2}\right|}{\theta^{n}}=\left|z_{1}-z_{2}\right|
\]
 so $\eta_{z_{1},z_{2}}$ is a quasiconvexity certificate.
\end{comment}

\end{enumerate}
\end{proof}

\section{The Cauliflower}
In this section $c=\frac 14$, and $f=f_{1/4}: z\mapsto z^2+ \frac 14$.
%The cauliflower has cusps at the landing points of the dyadic external rays, i.e. the points whose central itinerary has only finitely-many peripheral tracks.
% We use  the same certificates as in the hyperbolic case, but now it is trickier to show that they work.
Our goal is to prove the quasiconvexity of $\mathrm{Exterior}(\mathcal{J})$, \cref{quasiconvex-cauliflower}.
Unlike in the hyperbolic case, the postcritical set of $f$ has an accumulation point $p=\frac 12$ on $\mathcal J$. This complicates the argument because if the distance between iterates $w_1=f^{\circ n}(z_1)$ and $w_2=f^{\circ n}(z_2)$ is large in comparison to the distance between $w_1$ and $p$, then the distortion estimate on $f^{\circ (-n)}(\eta_{w_1,w_2})$ degenerates and we cannot deduce the quasiconvexity of the itinerary $\eta_{z_1,z_2}$ from the quasiconvexity of $\eta_{w_1,w_2}$. We provide a direct argument for this case.

\subsection{Itineraries have finite length}
We first need to know that each itinerary $\eta_{z_1,z_2}$ has a finite length. We will in fact show an exponential decay of the constituent tracks. For this to hold we need to glue together consecutive express tracks. This gluing is essential for having exponential decay, since the tracks of the central itinerary along the real line, $\eta_{\frac 12}$, decay at only a quadratic rate.

\begin{definition}
	The \emph{reduced decomposition} of an itinerary $\eta$ is the unique decomposition $\eta=\eta_1+\dots+\eta_k$ where each $\eta_i$ is a concatenation of express tracks followed by a single peripheral track.
\end{definition}

The following definition is used in the proof of \cref{prop:finite_length}.
\begin{definition}
	The \emph{shadow} of a station $s$ is the set of all terminals $z\in \mathcal J$ that are the endpoints of itineraries starting at $s$.
\end{definition}

Using this definition, we claim:
\begin{proposition} \label{prop:finite_length}
	Let $z \in \mathcal J$, and let $\eta_z=\eta_1+\dots+\eta_k$ be its reduced decomposition. Then we have $\Length(\eta_j)\lesssim \theta^j$ for some $\theta < 1$. In particular, $\Length(\eta_z)<\infty$ and all points $z\mathcal \in J$ are accessible from infinity.
\end{proposition}

\begin{proof}
The idea is that peripheral tracks never turn twice in the same direction, so cannot approach the cusp $p$ in a parabolic manner. Thus at large scales the length decays by a definite factor, and by the self-similarity of itineraries this follows also for the small-scale.
To make it rigorous, consider first for simplicity the reduced tracks that start at the main station $\s_{0,0}$ with at least three consecutive express tracks. Take a neighborhood $N$ of the union of all those tracks, which does not contain the critical point $0$ and on which $f$ is univalent.
The preimages of these tracks give all reduced tracks that start at some station $s$ with at least three express tracks.
By Koebe's distortion theorem, we have 
\begin{equation}
\diam(\shadow(s)) \asymp \dist (s,\mathcal J) \asymp \diam (N_s)
\end{equation}
where $N_s$ is the preimage of $N$ that sends the main station to $s$. Thus the length of $\eta_j$ decays at the same rate as $\dist(s,\mathcal J)$, which is exponential.

We used the assumption that the itinerary starts with at least three express tracks in order to have the neighborhood $N$. For itineraries that do not start with three consecutive express tracks, we consider separately the family $\Gamma_{\downarrow \downarrow \leftarrow}$ of those itineraries which start with two express tracks followed by a left itinerary, and $\Gamma_{\downarrow \downarrow \rightarrow}$. For each of these families the previous argument works.
\end{proof}

The shadows were not strictly necessary for the preceding proof, but they draw analogy with similar estimates for the Farey tesselation of the disk.

We now proceed to showing quasiconvexity of the itineraries, as sketched above. The purpose of the following definition is to organize points according to their distance from the main cusp in an $f$-invariant way. We decompose the points of $\mathcal J$ according to the first \emph{departure}\,: the first time that the central itinerary made a turn.
\input{"marker path 3.tex"}

\begin{definition}
Let $n \in \mathbb N$. We define the $n$-th \emph{departure set} $I_{n, \mathbb D} \subset \partial \mathbb D ^*$ to be the set of points $\zeta \in \partial \mathbb D^*$ whose central itinerary $\eta_{\zeta}$ starts with $n$ express tracks, followed by a peripheral track.
See \cref{fig:departure-decomposition}.
\end{definition}

This decomposition is invariant under $f_0$ in the sense that $f_0(I_{n+1, \mathbb D})=I_{n, \mathbb D}$, because of the invariance of $\eta _\zeta$.
Thus by applying the Böttcher map $\psi$ we obtain a corresponding departure decomposition $I_n = \psi(I_{n, \mathbb D})$ of $\mathcal J$ that is invariant under $f$.

%Fix a small ball $B$ around the main cusp $1/2$ and trace its preimages until we encounter the points $z_1,z_2$.

\subsection{Quasiconvexity for separated cusps}
We now show that the itineraries $\eta_{w_1,w_2}$ are certificates for points $w_1,w_2$ that satisfy the condition 
\begin{align} \label{parabolic separation}
	w_1 \in I_n, \quad w_2 \in I_m, \quad m-n \geq d,
\end{align}
where $d$ is a large enough integer, to be chosen later. This means that the points lie in well-separated cusps near the main cusp $p$.

Condition \eqref{parabolic separation} gives some control from below on $|w_1-w_2|$. We now bound the length of the itinerary $\psi(\eta)=\psi(\eta_{w_1,w_2})$ from above.
We represent $\psi(\eta)$ as a concatenation of three paths: the radial segment $\gamma_{m,n}=\psi([s_{m,0},s_{n,0}])$ and the two other components, $\gamma _m$ and $\gamma_n$. See \cref{fig:Three-parts-of-eta}.
Thus we have
\begin{equation}
	\Length(\psi(\eta))=\Length(\gamma_m)+\Length(\gamma_{m,n})+\Length(\gamma_n).
\end{equation}

\input{"departure-decomposition.tex"}

To estimate the length of each summand, we introduce $\ell_k = \Length(\psi([s_{k,0},s_{k+1,0}])) = \psi(s_{k,0})-\psi(s_{k+1,0}).$ 

\begin{lemma} \label{lem-ell_n}
	The lengths ${\ell_k}$ satisfy
	\begin{equation}
		\frac{\ell_k}{\ell_{k+1}} \asymp 1.
	\end{equation}
	In particular, for any constant $C \geq 0$ there is a sufficiently large integer $d$ such that
	\begin{align*}
		\Length(\gamma_{m,n}) = \ell_{m}+\ldots+\ell_{n} \\ \leq C (\ell_m+\ell_n)
	\end{align*}
	whenever $|m-n| \geq d$.
\end{lemma}
\begin{proof} \leavevmode
	The map $f$ is affinely conjugate to the map $z^2+z$, and the main cusp $\frac 12$ corresponds to $0$, hence $\ell_k \asymp \frac 1k$.
\end{proof}

%\begin{definition}
%The \emph{inner diameter} of a connected set $\Omega \subset \mathbb C$ is its diameter relative to the inner metric,
%\begin{equation}
%	\operatorname{InnerDiameter}(\Omega)=\sup _{p,q\in \Omega} \inf_\gamma \Length(\gamma)
%\end{equation}
%where the infimum is over all paths $\gamma$ in $\Omega$ that connect the point $p$ to $q$.
%\end{definition}
%
%We have the following:
%\begin{lemma}
%	\begin{equation*}
%		\operatorname{InnerDiameter}(\psi(I_n)) \lesssim \ell_n
%	\end{equation*}
%	where the hidden constant is independent of $n$.
%\end{lemma}

The condition $|m-n| \geq d$ prevents the line segment $\gamma _{m,n}$ from being small in comparison to the other two paths:
\begin{proposition} \leavevmode
	\emph{(i)} We have \begin{equation}
		\Length(\gamma_m) \lesssim \Length(\gamma_{m,n}).
	\end{equation}
	\emph{(ii)} For $d \gg 1$, 
	\begin{equation}
		\Length(\gamma_{m,n}) \lesssim |z_1-z_2|.
	\end{equation}
\end{proposition}

\begin{proof}
(i) 	Koebe's distortion theorem gives that 
\begin{equation}
		\Length(\gamma_m) \lesssim \ell_m
	\end{equation}
	by the invariance of both sides under $f^{-1}$.
	%In terms of $\ell _k$, we can write

(ii) By the triangle inequality and part (i),
\begin{align} \label{eq:triang}
	\begin{split}
	\Length(\gamma_{m,n}) \leq |w_1-w_2|+\Length(\gamma_m)+\Length(\gamma_n) %\nonumber
	\\ \leq |w_1-w_2|+C(\ell_m + \ell_n),
	\end{split}
\end{align}
for a constant $C \geq 0$ independent of $d$. Applying \cref{lem-ell_n} on this constant $C$ we get that for $d \gg 1$, 
\begin{align*}
\Length(\gamma_{m,n}) \lesssim \Length(\gamma_{m,n}) - C(\ell_m + \ell _n)
\end{align*}
which together with \eqref{eq:triang} concludes the proof.
\end{proof}

\begin{corollary}
	Let $d \gg 1$ be a positive integer. There exists a constant $A>0$ such that for every pair of points $w_1,w_2$ that satisfy \cref{parabolic separation}, the itinerary $\eta_{w_1,w_2}$ is $A$-quasiconvex.
\end{corollary}

\subsection{The Parabolic Elevator}

\begin{theorem} \label{quasiconvex-cauliflower} %\leavevmode
	\begin{enumerate}[label=\normalfont(\roman*)]
	The domain $\mathrm{Exterior}(\mathcal{J})$ is quasiconvex with the itineraries $\eta_{z_1,z_2}$ as certificates.
	\end{enumerate}
\end{theorem}

\begin{proof}[Proof. (Parabolic Conformal Elevator on $\mathcal J$)] \label{parabolic-elevator}
Let $d\gg 1$ be a sufficiently large integer and let $z_1,z_2 \in \mathcal J$ be a pair of points. Repeatedly apply $f$ on $z_1,z_2$ until one of the following two stopping conditions happens:
\begin{enumerate}[label=\normalfont(\roman*)]
	\item $\left|f^{\circ N}(z_1)-f^{\circ N}(z_2)\right|>\epsilon$, where $\epsilon=\epsilon(d)>0$ is a constant;		
	or
	\item $f^{\circ N }(z_1) \in I_n$ and $f^{\circ N }(z_2) \in I_m$ with $|m-n| \geq d$.		
\end{enumerate}

Denote $w_i=f^{\circ N}(z_i)$. We already proved that the itinerary $\eta_{w_1,w_2}$ satisfies
\begin{equation*}
	\Length(\eta_{w_1,w_2}) \leq A |w_1-w_2|
\end{equation*}
for some $A>0$. We now deduce that the original points $z_1,z_2$ enjoy a similar estimate,
\begin{equation*}
	\Length(\eta_{z_1,z_2}) \leq B |z_1-z_2|,
\end{equation*}
where $B$ depends only on $A$. This follows from Koebe's distortion theorem applied $N$ times on the univalent function $f^{-1}$, but some care is due in checking that the inverse branches at each step are defined in a neighborhood of the itinerary.

Fix a small ball $B_1=B(\frac 12, 0.1)$ around the main cusp. Its preimages are topological balls centered at all the cusps of $\mathcal J$, and we index them by $B_\zeta$ where $\zeta=\frac q{|q|}$ for a ball centered at $q$. Each ball $B_{\zeta}$ has a \emph{level}, which is the first iterate $k$ for which $f^{\circ k}(B_{\zeta}) = B$. Repeatedly applying $f^{-1}$ on the pair $w_1,w_2$ until we reach $z_1,z_2$, we get two sequences $B^1_k,B^2_k$ of balls with $B^1_1=B^2_1=B$. We consider separately the case where the sequences coincide and the case where they differ.

 Let $j$ be the first index where $B^1_1 \neq B^2_1$.
%We define the level of each of $z_1, z_2$ to be the level of the corresponding ball containing them.

%By the stopping criterion, 
%, which implies that
%	\begin{equation*}
%		|w_1-w_2| \lesssim |z_1-z_2| \cdot \|(f^{\circ N})'|_{\mathcal J}\|_{\infty}
%	\end{equation*}
%	and that
%	\begin{align*}
%		\Length (\eta_{w_1,w_2}) = \Length(f^{\circ N}(\eta_{z_1,z_2})) \\
%		\asymp \Length(\eta_{z_1,z_2}) \cdot |(f^{\circ N})'|.
%	\end{align*}
%	The conclusion follows. From now suppose that we are in case (ii).

Suppose we are in step (ii). By the choice of $w_1,w_2$, for every $k=0,\dots,N$ there is an annulus that separates $f^{\circ k}(z_1),f^{\circ k}(z_2)$ from the post-critical set of $f$, with modulus bounded from below uniformly in $N$.
Thus by Koebe's distortion we have 
\begin{align*}
|f^{\circ k}(z_1)-f^{\circ k}(z_2)|\geq c |z_1-z_2|
\end{align*}
for some constant $c>1$.

%Indeed, in this case there is an annulus of definite modulus that has both $z_1,z_2$ in its bounded complementary component and has all points of $\CriticalOrbit(f)$ in the unbounded complementary component.
%
%Instead of keeping track of the distance to $\mathrm{CriticalOrbit}(f)$, it is enough to consider the distance to the fixed point $1/2$, which is its only accumulation point on $\mathcal J$.
%
%Thus by repeatedly applying $f$ we either manage to separate $z_1,z_2$ a definite distance apart, in which case the argument for the hyperbolic case works, or we manage to make
%\begin{align*}
%\big|f^{\circ m} (z_1)-\tfrac 12\big| \leq c |f^{\circ m} (z_1)-f^{\circ m} (z_2)|
%\end{align*}
%for a constant $c$.
\end{proof}


%This concludes the proof.

\begin{comment}
\subsubsection*{Diameter Comparisons}

Denote by $\diam\left(A\right)$ the Euclidean diameter of a set $A$,
and by $i.\diam\left(A\right)$ the inner diameter on the escaping
set, i.e.\ the diameter induced by the Riemann mapping from the escaping
set to the disk.

\textbf{Claim. }$\diam T_{p,n}\asymp i.\diam T_{p,n}$.

\textbf{Claim. }$\diam U_{p,n}\asymp i.\diam U_{p,n}$.

\textbf{Observation. }Let $R>0$ be the distance from the post-critical
set to the Julia set. Consider the ball $B=B(z,\frac{R}{2})$.

Since $B$ is disjoint from the post-critical set, none of its preimages
$f^{-n}\left(B\right)$ contains the critical point $0$.

Thus $f$ restricted on each such preimage is univalent and 2-to-1.

By Koebe's distortion Theorem, applied to iterates $f^{\circ n}$,
the diameter of the preimages of $B$ changes by at most a multiplicative
constant.

This principle shows that all points $z$ on the Julia set $J(p_{c})$
are accessible, since after repeated applications of $f^{n}(B)$ we
get a topological ball of definite size which we may use to construct
an explicit path exiting $K$ in a rectifiable way.

\section{Accessibility in the Parabolic Case}

The basic strategy will be to investigate the geometry near the main
cusp $p=\frac{1}{4}$, since all other cusps are preimages of $p$
under $f$,

whence the principle of the conformal elevator reduces the general
case to the case of a point sufficiently close to the main cusp $p$.

To implement this strategy, we take some arbitrary other point on
the Julia set, connect it by a curve $\gamma$ to $a$, then consider
all preimages of $\gamma$.

In general, consecutive images near a parabolic point have consecutive
distances comparable to $\frac{1}{n^{2}}$ , where $n$ is the index
of the preimage.
\end{comment}

\bibliographystyle{acm}
\bibliography{quasiconvex_cauliflower}
\end{document}
