\input{preamble.tex}
\begin{document}

	
Lemma 1.1. Let $z_n$	 be a backwards orbit, meaning $f(z_2)=z_1$ and so on. Suppose that ...
Proof [lemma 1.1]. The map $f$ and all its backward iterates $f^ {\circ (-n)}$ are unramified outside of the post-critical set $PC$, so
$f: \hat{\mathbb C} \setminus PC(f) \to \hat{\mathbb C} \setminus PC(f)$ is a strict hyperbolic contraction.

	
The goal: 
1. 
Let $\Delta$ be a ball around $p$.
Every step that we are not in $\Delta$ we go down by a definite factor.

Because the hyperbolic distance is contracted by $\theta$.
THe hyperbolic distance is a local isometry by definition.
Just look at the derivative infinitesimally.
hyperbolic derivative of $f$

The inclusion $i: \hat{\mathbb C} \setminus PC(f) \to \hat{\mathbb C} \setminus f^{-1}(PC(f))$ is a strict contraction, so the composition $ f \circ i: \hat{\mathbb C} \setminus PC(f) \to \hat{\mathbb C} \setminus PC(f)$ is a strict contraction. 

In particular on $\mathcal J \setminus 1/2$. (It is not defined at the cusp.)
TO deal with this say that it i a contraction on the Julia set minus $\Delta /2$. Then the hyperbolic metric is bounded above there and we may use compactness. For every point in $J \setminus \Delta/2$ we have a strict contraction, so by compactness it is a strict contraction there.
"Even if we land in $\Delta$ every second step, we are still contracting every second step."

This is indeed an inclusion because $ \hat{\mathbb C} \setminus   \subset \hat{\mathbb C} \setminus f^{-1}(PC(f)) $, because 
$ PC(f) \supset f^{-1}(PC(f)) $

(Any holomorphic mapping between hyperbolic Riemann surfaces is a contraction)
\end{document}